### 2023-06-23 chapter_2/src/appendix.qmd
fix weird ppc graph thing

```{r}
#| label: fig-hypothesis-5-ppc
#| tbl-cap: Posterior Predictive checks for $H_5$

list_ppc[["h_5"]][["red"]]
list_ppc[["h_5"]][["blue"]]
```

>>>>

```{r}
#| label: fig-hypothesis-5-ppc
#| layout-ncol: 2
#| fig-cap: Posterior Predictive checks for $H_5$
#| fig-subcap:
#|   - Proportion of yard signs red
#|   - Proprotion of yard signs blue

list_ppc[["h_5"]][["red"]]$continuous
list_ppc[["h_5"]][["blue"]]$continuous
```
